Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-10-05 background.tex
2014.10.05 (Vassilis) Clean-up, rewording and reviewing the unstructured section. Efficiency, overhead and scalability definitions reworked in background section.

We employ both tabular and pictorial means to 
articulate features of the proposed methodologies and outline
both strengths and weaknesses.
To ascertain the effectiveness of each proposal, we predominantly use 
three criteria that capture the behavior of the algorithms 
discussed:
\emph{efficiency}, \emph{overhead} and \emph{scalability}.
For each of these criteria, we use a coarse-grained,
three-level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}.
Each criterion has its own
interpretation of the above literal values. 
\emph{Efficiency} means how well the
algorithm performs its search and topology adaptation functions. We also take
take into account how this might effect other characteristics of the networks
under consideration\footnote{For example we don't actually want a topologically
optimized BitTorrent swarm if this results in a degraded download performance,
a characteristic that is the protocol's corner stone.}.
%%VM Does the above sentence with the footnote now connect?
%%
%% PREVIOUS COMMENT AD I am not sure what the above line says.. or connects. Something is
%%	missing...

%% SOME ADDITIONAL EXAMPLES FOR EFFICIENCY IF WE WANT TO ADD THEM
%minimum-spanning-tree-based techniques have slow convergence speed in topology
%adaptation or the high clustering impacts load balancing and constrains search
%scope (or at least increases search satisfaction time), all reducing overall
%efficiency.

Moreover, efficiency is negatively effected every time an algorithm
reduces its search scope.
For the \emph{overhead} criterion, we evaluate the cost
to compute and communicate peer join, message forwarding, 
and topology maintenance. For example, when a protocol relies on peers
exchanging routing tables with other peers within a 2-hop radius with each other
, then we can be safelly deduce that it incurs lower overhead when compared to a
protocol that requires global knowledge of the overlay network.
%%VM Does the above sentence with the footnote now connect?
%%
%%PREVIOUS COMMENT AD Again I am not sure how the example above ties with the definition...
For the \emph{scalability} criterion, we consider system behavior 
with respect to the number of participating peers. 
We consider systems with low, medium, and high scalability 
to mean they can support hundreds, tenths of thousands, 
and millions of nodes, respectively.

>>>>

We employ both tabular and pictorial means to 
articulate features of the proposed methodologies and outline
both strengths and weaknesses.
To ascertain the effectiveness of each proposal, we predominantly use 
three criteria that capture the behavior of the algorithms 
discussed:
\emph{efficiency}, \emph{overhead} and \emph{scalability}.
For each of these criteria, we use a coarse-grained,
three-level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}.
Each criterion has its own
interpretation of the above literal values. 
\emph{Efficiency} means how well the
algorithm performs its search and topology adaptation functions. Our assessment
also considers any negative effects that might come along with the application
of the algorithm on intrinsic characteristics of the system (i.e., search scope
coverage, download performance e.t.c).
%% VM Reworked above definition for "efficiency".

For the \emph{overhead} criterion, we evaluate the cost
of computing and communicating peer join, message forwarding, 
and overlay topology maintenance. For instance, the overhead that an algorithm,
which needs global knowledge of the overlay topology, imposes to the system is
greater compared to a protocol that only relies on peers exchanging routing
tables within a a 2-hop radius from each other.
%%VM Reworked definition of overhead and explanatory sentence.
%%

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if the are proven to
effectivelly support hundreds, tenths of thousands or millions of nodes,
respectively.
%%%VM Reworked definition.
%%
